---
title: "ElectricVehicles"
---

### Electric Vehicles
Data comes from Washington State Department of Licensing and shows the number of Battery Electric and Plug-in Hybrid Vehicles currently registered in Washington state

This analysis uses parameterized markdown to show the state that the vehicle is now located and which counties have the highest number of electric vehicles with licenses from Washington State.

<a href="https://github.com/willavanliew/ParameterizedMarkdown" target="_blank">Associated Github Repository</a>
The table below shows each state and links to the html file with the associated map. 


```{r}
#| include: false
library(tidyverse)
library(shiny)
library(DT)
ds <- read.csv("https://data.wa.gov/api/views/f6w7-q2d2/rows.csv?accessType=DOWNLOAD")
```


```{r}
#| warning: false
electrics <- ds %>%
  group_by(State) %>%
  summarize(ElectricVehicles = n())


electric <- function(state){
  electrics %>%
    filter(State == state) %>%
    select(ElectricVehicles)
}

States <- data.frame(state_code = unique(ds$State), state_full = state.name[match(unique(ds$State),state.abb)]) 


States <- States %>%
  mutate(ElectricVehicles = unlist(map(state_code, electric)),
         state_full = case_when(
           state_code == "DC" ~ "Washington DC",
           state_code == "BC" ~ "British Columbia",
           TRUE ~ state_full),
         link = paste0("./files/", state_code,".html"),
         report = paste0('<a  target=_blank href=\'', link, '\' >', state_full,'</a>' ))
```

```{r}
States %>%
  select(report, ElectricVehicles) %>%
  datatable(States, 
          filter="top", 
          escape=FALSE, 
          colnames = c("Report", "# Electric Vehicles"),
          rownames = FALSE)
```
